---
pagetitle: "Table"
params:
  input: "input.tsv"
  prefix: "table"
---

```{r setup, include=FALSE}
library(tidyverse)
library(DT)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{r table, echo=FALSE}
df <- read_tsv(params$input)

datatable(
  df %>% mutate(across(where(~ is.character(.) && n_distinct(.) <= 10), as.factor)),
  escape = FALSE, selection = "none", rownames = FALSE,
  filter = 'top', extensions = "Buttons",
  options = list(
    pageLength = 10, dom = 'Blfrtip', autoWidth = FALSE,
    deferRender = TRUE, orderClasses = FALSE,
    buttons = list(
      list(extend = 'colvis', columns = 0:(ncol(df) - 1)),
      list(extend = 'csv',   filename = params$prefix),
      list(extend = 'excel', filename = params$prefix)
    )
  )
)
```

<style>
body { font-family: 'Segoe UI', system-ui, sans-serif; padding-top: 7px; }
.container, .main-container { width: 100% !important; max-width: 100% !important; }

/* ── DataTable ── */
table.dataTable tbody tr       { transition: background 0.12s; }
table.dataTable tbody tr:hover td { background-color: #f0faf0 !important; }
table.dataTable thead th       { background-color: #f6f6f6; border-bottom: 2px solid #49A942 !important; }
table.dataTable td, table.dataTable th {
  max-width: 200px;
  overflow: hidden;
  text-overflow: ellipsis;
  white-space: nowrap;
}
table.dataTable thead td {
  overflow: visible;
}

/* ── ColVis / Buttons ── */
.dt-buttons .dt-button {
  background: #2372B9 !important;
  color: white !important;
  border: none !important;
  border-radius: 4px !important;
  padding: 5px 14px !important;
  font-size: 13px !important;
  box-shadow: none !important;
  transition: background 0.15s !important;
}
.dt-buttons .dt-button:hover { background: #1a5899 !important; }
</style>
