---
pagetitle: "Sample Contamination Estimate"
params:
  input: "sample-contamination-estimate.tsv"
  prefix: "sce"
---

```{r setup, include=FALSE}
library(tidyverse)
library(DT)
library(plotly)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  WARN = FALSE
)
```

```{r load, include=FALSE}
df <-
  read_tsv(params$input, comment = "##") %>%
  rename_with(~ str_replace(., "^#", "")) %>%
  mutate(
    FLAG = case_when(
      CHARR > 0.03 | INCONSISTENT_AB_HET_RATE > 0.15 ~ "FAIL",
      CHARR > 0.02 | INCONSISTENT_AB_HET_RATE > 0.10 ~ "WARN",
      TRUE ~ "PASS"
    ),
    FLAG = factor(FLAG, levels = c("PASS", "WARN", "FAIL"))
  ) %>%
  select(SAMPLE, FLAG, CHARR, INCONSISTENT_AB_HET_RATE, everything())

flag_colours <- c(PASS = "#2ca02c", WARN = "#ff7f0e", FAIL = "#d62728")
```

<div class="report-header">
  <div class="report-header-title">Sample Contamination Estimation</div>
</div>

```{r plot, echo=FALSE}
p <- plot_ly(
  df,
  x             = ~CHARR,
  y             = ~INCONSISTENT_AB_HET_RATE,
  type          = "scatter",
  mode          = "markers",
  color         = ~FLAG,
  colors        = flag_colours,
  customdata    = ~SAMPLE,
  hovertemplate = "<b>%{customdata}</b><br>CHARR: %{x:.5f}<br>Inconsistent AB Het Rate: %{y:.5f}<extra></extra>",
  marker        = list(size = 9, opacity = 0.85, line = list(width = 0)),
  key           = ~SAMPLE
) %>%
  # empty highlight trace — always on top (added last)
  add_trace(
    type          = "scatter",
    mode          = "markers",
    x             = NULL,
    y             = NULL,
    customdata    = NULL,
    hoverinfo     = "skip",
    showlegend    = FALSE,
    marker        = list(size = 15, color = "rgba(0,0,0,0)",
                         line = list(color = "black", width = 2.5)),
    inherit       = FALSE,
    name          = "_highlight"
  ) %>%
  layout(
    xaxis  = list(title = "CHARR"),
    yaxis  = list(title = "Inconsistent AB Het Rate"),
    legend = list(title = list(text = "Flag")),
    shapes = list(
      list(type = "line", x0 = 0.02, x1 = 0.02,
           y0 = 0, y1 = 1, yref = "paper",
           line = list(color = "#ff7f0e", dash = "dot", width = 1)),
      list(type = "line", x0 = 0.03, x1 = 0.03,
           y0 = 0, y1 = 1, yref = "paper",
           line = list(color = "#d62728", dash = "dot", width = 1)),
      list(type = "line", x0 = 0, x1 = 1, xref = "paper",
           y0 = 0.10, y1 = 0.10,
           line = list(color = "#ff7f0e", dash = "dot", width = 1)),
      list(type = "line", x0 = 0, x1 = 1, xref = "paper",
           y0 = 0.15, y1 = 0.15,
           line = list(color = "#d62728", dash = "dot", width = 1))
    ),
    margin = list(t = 30)
  ) %>%
  partial_bundle()
p
```

```{r table, echo=FALSE}
dt <- datatable(
  df %>% mutate(across(where(~ is.character(.) && n_distinct(.) <= 10), as.factor)),
  escape = FALSE, selection = "single", rownames = FALSE,
  filter = 'top', extensions = "Buttons",
  options = list(
    pageLength = 10, dom = 'Blfrtip', autoWidth = FALSE,
    deferRender = TRUE, orderClasses = FALSE,
    buttons = list(
      list(extend = 'colvis', columns = 0:(ncol(df) - 1)),
      list(extend = 'csv',   filename = params$prefix),
      list(extend = 'excel', filename = params$prefix)
    )
  )
)
dt
```

<div class="ref-bar">
  <span>Lu et al. (2023) <em>CHARR efficiently estimates contamination from DNA sequencing data.</em> AJHG 110:12.
  <a href="https://doi.org/10.1016/j.ajhg.2023.10.011" target="_blank">doi:10.1016/j.ajhg.2023.10.011</a></span>
  <a href="https://github.com/HTGenomeAnalysisUnit/SCE-VCF" target="_blank">SCE-VCF on GitHub</a>
</div>

```{js highlight_point, echo=FALSE}
document.addEventListener('DOMContentLoaded', function() {
  var attempts = 0;
  var interval = setInterval(function() {
    var plotEl = document.querySelector('.plotly.html-widget');
    var tableEl = document.querySelector('table.dataTable');
    if (plotEl && tableEl && window.Plotly) {
      clearInterval(interval);
      setupInteraction(plotEl, tableEl);
    }
    if (++attempts >= 100) clearInterval(interval);
  }, 100);

  function setupInteraction(plotEl, tableEl) {
    var gd = document.getElementById(plotEl.id);

    // Index of the dedicated highlight trace (last trace, named "_highlight")
    function highlightTraceIdx() {
      for (var i = gd.data.length - 1; i >= 0; i--) {
        if (gd.data[i].name === '_highlight') return i;
      }
      return gd.data.length - 1;
    }

    $(tableEl).on('click', 'tbody tr', function() {
      var dtApi = $(tableEl).DataTable();
      var rowData = dtApi.row(this).data();
      if (!rowData) return;

      var sample = rowData[0]; // SAMPLE is first column

      // Find x/y for the selected sample across all data traces
      var hx = null, hy = null;
      var hlIdx = highlightTraceIdx();
      for (var t = 0; t < gd.data.length; t++) {
        if (t === hlIdx) continue;
        var keys = gd.data[t].key || [];
        for (var i = 0; i < keys.length; i++) {
          if (keys[i] === sample) {
            hx = [gd.data[t].x[i]];
            hy = [gd.data[t].y[i]];
            break;
          }
        }
        if (hx !== null) break;
      }

      Plotly.restyle(gd, { x: [hx], y: [hy] }, [hlIdx]);
    });
  }
});
```

<style>
body { font-family: 'Segoe UI', system-ui, sans-serif; padding-top: 0; margin: 0; }

/* ── Page header ── */
.report-header {
  display: flex;
  align-items: baseline;
  gap: 14px;
  padding: 8px 4px 6px;
  border-bottom: 2px solid #49A942;
  margin-bottom: 8px;
}
.report-header-title {
  font-size: 1.6rem;
  font-weight: 600;
  color: #1a1a1a;
  letter-spacing: 0.01em;
}
.container, .main-container { width: 100% !important; max-width: 100% !important; margin: 0 !important; padding: 4px 8px !important; }

/* ── DataTable ── */
table.dataTable tbody tr       { transition: background 0.12s; }
table.dataTable tbody tr:hover td { background-color: #f0faf0 !important; }
table.dataTable tbody tr.selected td { background-color: #dff0d8 !important; }
table.dataTable thead th       { background-color: #f6f6f6; border-bottom: 2px solid #49A942 !important; }
table.dataTable td, table.dataTable th {
  max-width: 200px;
  overflow: hidden;
  text-overflow: ellipsis;
  white-space: nowrap;
}
table.dataTable thead td {
  overflow: visible;
}

/* ── ColVis / Buttons ── */
.dt-buttons .dt-button {
  background: #2372B9 !important;
  color: white !important;
  border: none !important;
  border-radius: 4px !important;
  padding: 5px 14px !important;
  font-size: 13px !important;
  box-shadow: none !important;
  transition: background 0.15s !important;
}
.dt-buttons .dt-button:hover { background: #1a5899 !important; }

/* ── Reference bar ── */
.ref-bar {
  display: flex;
  justify-content: space-between;
  align-items: center;
  font-size: 12px;
  color: #666;
  border-top: 1px solid #e0e0e0;
  margin-top: 18px;
  padding-top: 8px;
}
.ref-bar a { color: #2372B9; text-decoration: none; white-space: nowrap; }
.ref-bar a:hover { text-decoration: underline; }
</style>
