
```{r include=FALSE}
library(tidyverse)
library(DT)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

```{=html}
<div id="app-header">
  <span id="app-title">CAVALIER Variant Viewer</span>
</div>
```

```{r include=FALSE}

default_cols <-
  c('family_id', 'SYMBOL', 'CHROM', 'POS', 'REF', 'ALT', 'Consequence', 'IMPACT', 'gnomad_AF', 'CADD')

variants <-
  read_csv('short_candidates.csv') %>% 
  select(all_of(default_cols), everything()) %>%
  group_by(family_id) %>% 
  mutate(
    pdf    = file.path('by_family', family_id, str_c(family_id, '.pdf')),
    html   = file.path('by_family', family_id, str_c(family_id, '.igv_report.html')),
    row_id = row_number() - 1L
  ) %>% 
  ungroup()

default_cols_struc <-
  c('family_id', 'SYMBOL', 'CHROM', 'POS', 'END', 'SVTYPE', 'Consequence', 'IMPACT', 'Max_AF')

struc_variants <-
  read_csv('struc_candidates.csv')  %>%
  select(all_of(default_cols_struc), everything()) %>%
  mutate(
    pdf     = file.path('by_family', family_id, str_c(family_id, '.pdf')),
    samplot = file.path('by_family', family_id, 'samplot', str_c('samplot_', family_id, '_', variant_id,  '.png')),
    svpv    = file.path('by_family', family_id, 'svpv', family_id, SVTYPE, str_c(CHROM, '_', POS),
                        str_c(CHROM, POS, SVTYPE, '*.pdf', sep = '.')) %>%
      map_chr(~ first(list.files(dirname(.), pattern = basename(.), full.names = T) )),
  )

# Build columnDefs and ColVis targets for a dataframe with n_default visible cols
# and 3 trailing internal cols (hidden, excluded from ColVis)
dt_coldefs <- function(df, n_default) {
  n        <- ncol(df)
  internal <- (n - 3):(n - 1)
  extra    <- if (n > n_default + 3) n_default:(n - 4) else integer(0)
  defs     <- list(list(visible = FALSE, targets = internal))
  if (length(extra) > 0) defs <- c(defs, list(list(visible = FALSE, targets = extra)))
  list(col_defs = defs, colvis_targets = 0:(n - 4))
}

```

```{=html}
<div id="vtype-container" class="vtype-container">
  <div class="tab-bar">
    <button class="tab-btn active" data-tab="vtab-short">Short Variants</button>
    <button class="tab-btn"        data-tab="vtab-struc">Structural Variants</button>
  </div>
  <div id="tab-vtab-short" class="tab-panel active" style="padding:12px;">
```

```{r echo=FALSE}
cd <- dt_coldefs(variants, length(default_cols))
datatable(
  variants %>% mutate(across(where(~ is.character(.) && n_distinct(.) <= 10), as.factor)),
  escape = FALSE, selection = "none", rownames = FALSE,
  filter = 'top', extensions = "Buttons",
  options = list(
    pageLength = 10, dom = 'Blfrtip', autoWidth = FALSE,
    buttons = list(list(extend = 'colvis', columns = cd$colvis_targets)),
    columnDefs = cd$col_defs,
    rowCallback = JS("
      function(row, data) {
        var n = data.length;
        $(row).attr('data-pdf',    data[n-3]);
        $(row).attr('data-html',   data[n-2]);
        $(row).attr('data-row-id', data[n-1]);
        $(row).css('cursor', 'pointer');
      }
    ")
  ),
  callback = JS("
    table.on('click', 'tbody tr', function() {
      table.$('tr.selected-row').removeClass('selected-row');
      $(this).addClass('selected-row');
      loadSample($(this).data('pdf'), $(this).data('html'), Number($(this).data('row-id')));
    });
    $(table.table().body()).find('tr:first').trigger('click');
  ")
)
```

```{=html}
  </div>
  <div id="tab-vtab-struc" class="tab-panel active" style="padding:12px;">
```

```{r echo=FALSE}
cd_s <- dt_coldefs(struc_variants, length(default_cols_struc))
datatable(
  struc_variants %>% mutate(across(where(~ is.character(.) && n_distinct(.) <= 10), as.factor)),
  escape = FALSE, selection = "none", rownames = FALSE,
  filter = 'top', extensions = "Buttons",
  options = list(
    pageLength = 10, dom = 'Blfrtip', autoWidth = FALSE,
    buttons = list(list(extend = 'colvis', columns = cd_s$colvis_targets)),
    columnDefs = cd_s$col_defs,
    rowCallback = JS("
      function(row, data) {
        var n = data.length;
        $(row).attr('data-pdf',     data[n-3]);
        $(row).attr('data-samplot', data[n-2]);
        $(row).attr('data-svpv',    data[n-1]);
        $(row).css('cursor', 'pointer');
      }
    ")
  ),
  callback = JS("
    table.on('click', 'tbody tr', function() {
      table.$('tr.selected-row').removeClass('selected-row');
      $(this).addClass('selected-row');
      loadStrucSample($(this).data('pdf'), $(this).data('samplot'), $(this).data('svpv'));
    });
  ")
)
```

```{=html}
  </div>
</div>
```

```{=html}
<div style="margin-top: 28px;">

  <div id="viewer-short" class="viewer-container" style="display:none;">
    <div class="tab-bar">
      <button class="tab-btn active" data-tab="slides">Slides</button>
      <button class="tab-btn"        data-tab="igv">IGV</button>
    </div>
    <div id="tab-slides" class="tab-panel active">
      <iframe id="viewer-pdf" width="100%" height="800px" style="border:none;"></iframe>
    </div>
    <div id="tab-igv" class="tab-panel">
      <iframe id="viewer-igv" width="100%" height="800px" style="border:none;"></iframe>
    </div>
  </div>

  <div id="viewer-struc" class="viewer-container" style="display:none;">
    <div class="tab-bar">
      <button class="tab-btn active" data-tab="struc-slides">Slides</button>
      <button class="tab-btn"        data-tab="samplot">SAMPLOT</button>
      <button class="tab-btn"        data-tab="svpv">SVPV</button>
    </div>
    <div id="tab-struc-slides" class="tab-panel active">
      <iframe id="viewer-struc-pdf" width="100%" height="800px" style="border:none;"></iframe>
    </div>
    <div id="tab-samplot" class="tab-panel">
      <img id="viewer-samplot" width="100%" style="display:block;">
    </div>
    <div id="tab-svpv" class="tab-panel">
      <iframe id="viewer-svpv" width="100%" height="800px" style="border:none;"></iframe>
    </div>
  </div>

</div>
```

<style>
/* ── Global ── */
body { font-family: 'Segoe UI', system-ui, sans-serif; }

/* ── Header ── */
#app-header {
  background-color: #49A942;
  color: white;
  padding: 14px 28px;
  margin-bottom: 28px;
  box-shadow: 0 2px 6px rgba(0,0,0,0.18);
  display: flex;
  align-items: center;
  gap: 14px;
}
#app-header::before {
  content: '';
  display: inline-block;
  width: 5px;
  height: 28px;
  background: #ECE953;
  border-radius: 3px;
  flex-shrink: 0;
}
#app-title {
  font-size: 22px;
  font-weight: 700;
  letter-spacing: 0.4px;
  color: white;
}

/* ── DataTable ── */
table.dataTable tbody tr       { transition: background 0.12s; }
table.dataTable tbody tr:hover td { background-color: #f0faf0 !important; }
tr.selected-row td             { background-color: #d6f0d5 !important; }
table.dataTable thead th       { background-color: #f6f6f6; border-bottom: 2px solid #49A942 !important; }
table.dataTable td, table.dataTable th {
  max-width: 200px;
  overflow: hidden;
  text-overflow: ellipsis;
  white-space: nowrap;
}

/* ── ColVis / Buttons ── */
.dt-buttons .dt-button {
  background: #2372B9 !important;
  color: white !important;
  border: none !important;
  border-radius: 4px !important;
  padding: 5px 14px !important;
  font-size: 13px !important;
  box-shadow: none !important;
  transition: background 0.15s !important;
}
.dt-buttons .dt-button:hover { background: #1a5899 !important; }

/* ── Containers (vtype + viewer) ── */
.vtype-container, .viewer-container {
  border: 1px solid #dee2e6;
  border-radius: 0 6px 6px 6px;
  box-shadow: 0 3px 10px rgba(0,0,0,0.08);
}
.vtype-container  { margin-bottom: 28px; }
.viewer-container { overflow: hidden; }

/* ── Tab bar ── */
.tab-bar {
  display: flex;
  gap: 4px;
  border-bottom: 2px solid #49A942;
  background: #f4f4f4;
  padding: 8px 8px 0;
  margin-bottom: 0;
}
.tab-btn {
  padding: 8px 24px;
  border: 1px solid transparent;
  border-bottom: none;
  border-radius: 4px 4px 0 0;
  background: transparent;
  cursor: pointer;
  font-size: 14px;
  font-weight: 500;
  color: #555;
  position: relative;
  bottom: -2px;
  transition: color 0.15s, background 0.15s;
}
.tab-btn:hover:not(.active) { background: #e4e4e4; color: #333; }
.tab-btn.active {
  background: white;
  border-color: #49A942;
  color: #2372B9;
  font-weight: 600;
}
.tab-panel        { display: none; }
.tab-panel.active { display: block; }

.container      { width: 100% !important; max-width: 100% !important; }
.main-container { width: 95% !important; max-width: 95% !important; }
</style>

<script>
var _pendingIgv       = null;
var _pendingSvpv      = null;
var _pdfTimeout       = null;
var _strucPdfTimeout  = null;
var _igvAbortCtrl     = null;
var _activeTabs  = { 'vtype-container': 'vtab-short', 'viewer-short': 'slides', 'viewer-struc': 'struc-slides' };

// Both panels start visible so DataTables can measure column widths during init.
// After DT's $(document).ready() has run, hide the struc panel.
$(document).ready(function() {
  document.getElementById('tab-vtab-struc').classList.remove('active');
});

function switchTab(container, tab) {
  container.querySelectorAll('.tab-btn').forEach(function(b) { b.classList.remove('active'); });
  container.querySelectorAll('.tab-panel').forEach(function(p) { p.classList.remove('active'); });
  container.querySelector('[data-tab="' + tab + '"]').classList.add('active');
  document.getElementById('tab-' + tab).classList.add('active');
}

// All tab switching
document.addEventListener('click', function(e) {
  if (!e.target.matches('.tab-btn')) return;
  var tab       = e.target.getAttribute('data-tab');
  var container = e.target.closest('.viewer-container, .vtype-container');
  _activeTabs[container.id] = tab;
  switchTab(container, tab);

  // Vtype tab: reset viewers and auto-select first row
  if (tab === 'vtab-short' || tab === 'vtab-struc') {
    document.getElementById('viewer-short').style.display = 'none';
    document.getElementById('viewer-struc').style.display = 'none';
    var panelId = 'tab-' + tab;
    $('#' + panelId + ' table tbody tr:first').trigger('click');
    return;
  }

  // Viewer tab lazy loads
  if (tab === 'igv' && _pendingIgv) {
    loadSubsettedIframe(_pendingIgv.htmlUrl, _pendingIgv.rowId, 'viewer-igv');
    _pendingIgv = null;
  }
  if (tab === 'svpv' && _pendingSvpv) {
    document.getElementById('viewer-svpv').src = _pendingSvpv;
    _pendingSvpv = null;
  }
});

function loadSample(pdfUrl, htmlUrl, rowId) {
  document.getElementById('viewer-short').style.display = 'block';

  var pdfIframe = document.getElementById('viewer-pdf');
  pdfIframe.removeAttribute('srcdoc');
  pdfIframe.src = '';
  clearTimeout(_pdfTimeout);
  _pdfTimeout = setTimeout(function() { pdfIframe.src = pdfUrl; }, 50);

  var igvIframe = document.getElementById('viewer-igv');
  igvIframe.removeAttribute('srcdoc');
  igvIframe.src = '';

  var activeTab = _activeTabs['viewer-short'];
  if (activeTab === 'igv') {
    loadSubsettedIframe(htmlUrl, rowId, 'viewer-igv');
    _pendingIgv = null;
  } else {
    _pendingIgv = { htmlUrl: htmlUrl, rowId: rowId };
  }
  switchTab(document.getElementById('viewer-short'), activeTab);
}

function loadStrucSample(pdfUrl, samplotUrl, svpvUrl) {
  document.getElementById('viewer-struc').style.display = 'block';

  var strucPdfIframe = document.getElementById('viewer-struc-pdf');
  strucPdfIframe.src = '';
  clearTimeout(_strucPdfTimeout);
  _strucPdfTimeout = setTimeout(function() { strucPdfIframe.src = pdfUrl; }, 50);

  document.getElementById('viewer-samplot').src = samplotUrl;

  var svpvIframe = document.getElementById('viewer-svpv');
  svpvIframe.src = '';
  var activeTab = _activeTabs['viewer-struc'];
  if (activeTab === 'svpv') {
    svpvIframe.src = svpvUrl;
    _pendingSvpv = null;
  } else {
    _pendingSvpv = svpvUrl;
  }
  switchTab(document.getElementById('viewer-struc'), activeTab);
}

async function loadSubsettedIframe(htmlUrl, keepId, iframeId) {
  if (_igvAbortCtrl) _igvAbortCtrl.abort();
  _igvAbortCtrl = new AbortController();
  const signal = _igvAbortCtrl.signal;

  let html;
  try {
    html = await fetch(htmlUrl, { signal }).then(r => r.text());
  } catch (e) {
    if (e.name === 'AbortError') return;
    throw e;
  }

  // Subset and reindex tableJson rows
  html = html.replace(
    /("rows"\s*:\s*\[)(\[[\s\S]*?\])(\s*\]\s*\})/,
    function(_, prefix, rows, suffix) {
      const match   = rows.match(new RegExp('\\[' + keepId + ',[^\\]]*\\]'));
      const cleaned = match ? match[0].replace(/^\[\d+,/, '[0,') : '';
      return prefix + cleaned + suffix;
    }
  );

  // Subset and reindex sessionDictionary
  html = html.replace(
    /(const sessionDictionary\s*=\s*\{)([^<]*?)(\s*\})/,
    function(_, prefix, body, suffix) {
      const match   = body.match(new RegExp('"' + keepId + '"\\s*:\\s*"data:[^"]*"'));
      const cleaned = match ? '"0": ' + match[0].replace(/^"\d+"\s*:\s*/, '') : '';
      return prefix + cleaned + suffix;
    }
  );

  document.getElementById(iframeId).srcdoc = html;
}
</script>