---
pagetitle: "Variant Browser"
---

```{r setup, include=FALSE}
library(tidyverse)
library(DT)

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

# Build columnDefs and ColVis targets for a dataframe with n_default visible cols
# and n_internal trailing internal cols (hidden, excluded from ColVis)
dt_coldefs <- function(df, n_default, n_internal = 3) {
  n        <- ncol(df)
  internal <- (n - n_internal):(n - 1)
  extra    <- if (n > n_default + n_internal) n_default:(n - n_internal - 1) else integer(0)
  defs     <- list(list(visible = FALSE, targets = internal))
  if (length(extra) > 0) defs <- c(defs, list(list(visible = FALSE, targets = extra)))
  list(col_defs = defs, colvis_targets = 0:(n - n_internal - 1))
}
```

```{=html}
<div id="app-header">
  <span id="app-title">CAVALIER Variant Browser</span>
</div>

<div id="vtype-container" class="vtype-container">
  <div class="tab-bar">
    <button class="tab-btn active" data-tab="vtab-short">Short Variants</button>
    <button class="tab-btn"        data-tab="vtab-struc">Structural Variants</button>
  </div>
  <div id="tab-vtab-short" class="tab-panel active" style="padding:12px;">
```
```{r load_short, include=FALSE}
default_cols <-
  c('family_id', 'SYMBOL', 'CHROM', 'POS', 'REF', 'ALT', 'Consequence', 'IMPACT', 'gnomad_AF', 'CADD')

variants <-
  read_csv('short_candidates.csv') %>%
  select(all_of(default_cols), everything()) %>%
  group_by(family_id) %>%
  mutate(
    pdf  = file.path('by_family', family_id, 'varslides', str_c('.*', variant_id, '.*.pdf'))  %>%
      map_chr(~ first(list.files(dirname(.), pattern = basename(.), full.names = T))),
    html   = file.path('by_family', family_id, str_c(family_id, '.igv_report.html')),
    row_id = row_number() - 1L
  ) %>%
  ungroup() %>%
  mutate(
    ucsc_url = {
      track <- str_c(
        'track name="', VARIANT_CLASS, '" visibility=2 color=0,0,255\n',
        CHROM, " ", POS, " ", POS +1L
      )
      str_c(
        "https://genome.ucsc.edu/cgi-bin/hgTracks?db=hg38&",
        "position=", CHROM, ":", POS - 250, "-", POS + 250, "&",
        "hgt.customText=", URLencode(track)
      )
    },
    ucsc_render_url = str_replace(ucsc_url, 'hgTracks', 'hgRenderTracks')
  )

cd <- dt_coldefs(variants, length(default_cols), n_internal = 5)
```

```{r show_short, echo=FALSE}
datatable(
  variants %>% mutate(across(where(~ is.character(.) && n_distinct(.) <= 10), as.factor)),
  escape = FALSE, selection = "none", rownames = FALSE,
  filter = 'top', extensions = "Buttons",
  options = list(
    pageLength = 10, dom = 'Blfrtip', autoWidth = FALSE,
    buttons = list(list(extend = 'colvis', columns = cd$colvis_targets)),
    columnDefs = cd$col_defs,
    rowCallback = JS("
      function(row, data) {
        var n = data.length;
        $(row).attr('data-pdf',             data[n-5]);
        $(row).attr('data-html',            data[n-4]);
        $(row).attr('data-row-id',          data[n-3]);
        $(row).attr('data-ucsc-url',        data[n-2]);
        $(row).attr('data-ucsc-render-url', data[n-1]);
        $(row).css('cursor', 'pointer');
      }
    ")
  ),
  callback = JS("
    table.on('click', 'tbody tr', function() {
      table.$('tr.selected-row').removeClass('selected-row');
      $(this).addClass('selected-row');
      loadSample(
        $(this).data('pdf'), $(this).data('html'), Number($(this).data('row-id')),
        $(this).data('ucsc-url'), $(this).data('ucsc-render-url')
      );
    });
  ")
)
```

```{=html}
  </div>
  <div id="tab-vtab-struc" class="tab-panel active" style="padding:12px;">
```

```{r load_struc, include=FALSE}
default_cols_struc <-
  c('family_id', 'SYMBOL', 'CHROM', 'POS', 'END', 'SVTYPE', 'SVLEN', 'Consequence', 'IMPACT', 'Max_AF')

struc_variants <-
  read_csv("struc_candidates.csv") %>%
  select(all_of(default_cols_struc), everything()) %>%
  mutate(
    pdf = file.path("by_family", family_id, "varslides", str_c(".*", variant_id, ".*.pdf")) %>%
      map_chr(~ first(list.files(dirname(.), pattern = basename(.), full.names = T))),
    samplot = file.path("by_family", family_id, "samplot", str_c("samplot_", family_id, "_", variant_id, ".png")),
    svpv = file.path(
      "by_family", family_id, "svpv", family_id, SVTYPE, str_c(CHROM, "_", POS),
      str_c(CHROM, POS, SVTYPE, "*.pdf", sep = ".")
    ) %>%
      map_chr(~ first(list.files(dirname(.), pattern = basename(.), full.names = T))),
  ) %>%
  mutate(
    ucsc_url = {
      colour <- case_when(
        SVTYPE == "DEL" ~ "255,0,0",
        SVTYPE == "DUP" ~ "0,255,0",
        TRUE ~ "0,0,255"
      )
      width <- pmax(250, END - POS)
      track <- str_c(
        'track name="', SVTYPE, '" visibility=2 color=', colour, "\n",
        CHROM, " ", POS, " ", coalesce(END, POS + 1)
      )
      str_c(
        "https://genome.ucsc.edu/cgi-bin/hgTracks?db=hg38&",
        "position=", CHROM, ":", POS - width, "-", END + width, "&",
        "hgt.customText=", URLencode(track)
      )
    },
    ucsc_render_url = str_replace(ucsc_url, 'hgTracks', 'hgRenderTracks')
  )

cd_s <- dt_coldefs(struc_variants, length(default_cols_struc), n_internal = 5)
```

```{r show_struc, echo=FALSE}
datatable(
  struc_variants %>% mutate(across(where(~ is.character(.) && n_distinct(.) <= 10), as.factor)),
  escape = FALSE, selection = "none", rownames = FALSE,
  filter = 'top', extensions = "Buttons",
  options = list(
    pageLength = 10, dom = 'Blfrtip', autoWidth = FALSE,
    buttons = list(list(extend = 'colvis', columns = cd_s$colvis_targets)),
    columnDefs = cd_s$col_defs,
    rowCallback = JS("
      function(row, data) {
        var n = data.length;
        $(row).attr('data-pdf',              data[n-5]);
        $(row).attr('data-samplot',          data[n-4]);
        $(row).attr('data-svpv',             data[n-3]);
        $(row).attr('data-ucsc-url',         data[n-2]);
        $(row).attr('data-ucsc-render-url',  data[n-1]);
        $(row).css('cursor', 'pointer');
      }
    ")
  ),
  callback = JS("
    table.on('click', 'tbody tr', function() {
      table.$('tr.selected-row').removeClass('selected-row');
      $(this).addClass('selected-row');
      loadStrucSample(
        $(this).data('pdf'), $(this).data('samplot'), $(this).data('svpv'),
        $(this).data('ucsc-url'), $(this).data('ucsc-render-url')
      );
    });
  ")
)
```

```{=html}
  </div>
</div>

<div style="margin-top: 28px;">

  <div id="viewer-short" class="viewer-container">
    <div class="tab-bar">
      <button class="tab-btn active" data-tab="slides">Slides</button>
      <button class="tab-btn"        data-tab="igv">IGV</button>
      <button class="tab-btn"        data-tab="ucsc-short">Genome Browser</button>
    </div>
    <div id="tab-slides" class="tab-panel active">
      <iframe id="viewer-pdf" width="100%" height="800px" style="border:none;"></iframe>
    </div>
    <div id="tab-igv" class="tab-panel">
      <iframe id="viewer-igv" width="100%" height="800px" style="border:none;"></iframe>
      <p class="citation"><a href="https://doi.org/10.1093/bioinformatics/btac830" target="_blank">Robinson et al. (2022) Bioinformatics. doi:10.1093/bioinformatics/btac830</a></p>
    </div>
    <div id="tab-ucsc-short" class="tab-panel">
      <div style="padding: 10px 12px 0;">
        <a id="ucsc-link-short" href="#" target="_blank" class="ucsc-btn">Open interactive UCSC Genome Browser</a>
      </div>
      <iframe id="viewer-ucsc-short" width="100%" height="800px" style="border:none;"></iframe>
      <p class="citation"><a href="https://doi.org/10.1093/nar/gkaf1250" target="_blank">Casper et al. (2025) Nucleic Acids Research. doi:10.1093/nar/gkaf1250</a></p>
    </div>
  </div>

  <div id="viewer-struc" class="viewer-container" style="display:none;">
    <div class="tab-bar">
      <button class="tab-btn active" data-tab="struc-slides">Slides</button>
      <button class="tab-btn"        data-tab="svpv">SVPV</button>
      <button class="tab-btn"        data-tab="samplot">SAMPLOT</button>
      <button class="tab-btn"        data-tab="ucsc">Genome Browser</button>
    </div>
    <div id="tab-struc-slides" class="tab-panel active">
      <iframe id="viewer-struc-pdf" width="100%" height="800px" style="border:none;"></iframe>
    </div>
    <div id="tab-svpv" class="tab-panel">
      <iframe id="viewer-svpv" width="100%" height="800px" style="border:none;"></iframe>
      <p class="citation"><a href="https://doi.org/10.1093/bioinformatics/btx117" target="_blank">Munro et al. (2017) Bioinformatics. doi:10.1093/bioinformatics/btx117</a></p>
    </div>
    <div id="tab-samplot" class="tab-panel">
      <img id="viewer-samplot" width="100%" style="display:block;">
      <p class="citation"><a href="https://doi.org/10.1186/s13059-021-02380-5" target="_blank">Belyeu et al. (2021) Genome Biology. doi:10.1186/s13059-021-02380-5</a></p>
    </div>
    <div id="tab-ucsc" class="tab-panel">
      <div style="padding: 10px 12px 0;">
        <a id="ucsc-link" href="#" target="_blank" class="ucsc-btn">Open interactive UCSC Genome Browser</a>
      </div>
      <iframe id="viewer-ucsc" width="100%" height="800px" style="border:none;"></iframe>
      <p class="citation"><a href="https://doi.org/10.1093/nar/gkaf1250" target="_blank">Casper et al. (2025) Nucleic Acids Research. doi:10.1093/nar/gkaf1250</a></p>
    </div>
  </div>

</div>
```

<style>
/* ── Global ── */
body { font-family: 'Segoe UI', system-ui, sans-serif; }

/* ── Header ── */
#app-header {
  background-color: #49A942;
  color: white;
  padding: 14px 28px;
  margin-bottom: 28px;
  box-shadow: 0 2px 6px rgba(0,0,0,0.18);
  display: flex;
  align-items: center;
  gap: 14px;
  border-radius: 4px;
}
#app-title {
  font-size: 22px;
  font-weight: 700;
  letter-spacing: 0.4px;
  color: white;
}

/* ── DataTable ── */
table.dataTable tbody tr       { transition: background 0.12s; }
table.dataTable tbody tr:hover td { background-color: #f0faf0 !important; }
tr.selected-row td             { background-color: #d6f0d5 !important; }
table.dataTable thead th       { background-color: #f6f6f6; border-bottom: 2px solid #49A942 !important; }
table.dataTable td, table.dataTable th {
  max-width: 200px;
  overflow: hidden;
  text-overflow: ellipsis;
  white-space: nowrap;
}

/* ── ColVis / Buttons ── */
.dt-buttons .dt-button {
  background: #2372B9 !important;
  color: white !important;
  border: none !important;
  border-radius: 4px !important;
  padding: 5px 14px !important;
  font-size: 13px !important;
  box-shadow: none !important;
  transition: background 0.15s !important;
}
.dt-buttons .dt-button:hover { background: #1a5899 !important; }

/* ── Containers (vtype + viewer) ── */
.vtype-container, .viewer-container {
  border: 1px solid #dee2e6;
  border-radius: 0 6px 6px 6px;
  box-shadow: 0 3px 10px rgba(0,0,0,0.08);
}
.vtype-container  { margin-bottom: 28px; }
.viewer-container { overflow: hidden; }

/* ── Tab bar ── */
.tab-bar {
  display: flex;
  gap: 4px;
  border-bottom: 2px solid #49A942;
  background: #f4f4f4;
  padding: 8px 8px 0;
  margin-bottom: 0;
}
.tab-btn {
  padding: 8px 24px;
  border: 1px solid transparent;
  border-bottom: none;
  border-radius: 4px 4px 0 0;
  background: transparent;
  cursor: pointer;
  font-size: 14px;
  font-weight: 500;
  color: #555;
  position: relative;
  bottom: -2px;
  transition: color 0.15s, background 0.15s;
}
.tab-btn:hover:not(.active) { background: #e4e4e4; color: #333; }
.tab-btn.active {
  background: white;
  border-color: #49A942;
  color: #2372B9;
  font-weight: 600;
}
.tab-panel        { display: none; }
.tab-panel.active { display: block; }

.container      { width: 100% !important; max-width: 100% !important; }
.main-container { width: 95% !important; max-width: 95% !important; }

.citation {
  font-size: 11px;
  color: #888;
  margin: 4px 12px 6px;
}
.citation a { color: #888; }
.citation a:hover { color: #555; }

.ucsc-btn {
  display: inline-block;
  background: #2372B9;
  color: white !important;
  text-decoration: none;
  padding: 6px 16px;
  border-radius: 4px;
  font-size: 13px;
  font-weight: 500;
  margin-bottom: 8px;
  transition: background 0.15s;
}
.ucsc-btn:hover { background: #1a5899; }
</style>

<script>
var _pendingIgv       = null;
var _pendingSvpv      = null;
var _pendingUcscShort = null;
var _pendingUcsc      = null;
var _pdfTimeout       = null;
var _strucPdfTimeout  = null;
var _activeTabs = { 'vtype-container': 'vtab-short', 'viewer-short': 'slides', 'viewer-struc': 'struc-slides' };

// Both panels start visible so DataTables can measure column widths during init.
// After DT's $(document).ready() has run, hide the struc panel.
$(document).ready(function() {
  document.getElementById('tab-vtab-struc').classList.remove('active');
});

function switchTab(container, tab) {
  container.querySelectorAll('.tab-btn').forEach(function(b) { b.classList.remove('active'); });
  container.querySelectorAll('.tab-panel').forEach(function(p) { p.classList.remove('active'); });
  container.querySelector('[data-tab="' + tab + '"]').classList.add('active');
  document.getElementById('tab-' + tab).classList.add('active');
}

// All tab switching
document.addEventListener('click', function(e) {
  if (!e.target.matches('.tab-btn')) return;
  var tab       = e.target.getAttribute('data-tab');
  var container = e.target.closest('.viewer-container, .vtype-container');
  _activeTabs[container.id] = tab;
  switchTab(container, tab);

  // Vtype tab: show the matching viewer, hide the other
  if (tab === 'vtab-short' || tab === 'vtab-struc') {
    document.getElementById('viewer-short').style.display = tab === 'vtab-short' ? '' : 'none';
    document.getElementById('viewer-struc').style.display = tab === 'vtab-struc' ? '' : 'none';
    return;
  }

  // Viewer tab lazy loads
  if (tab === 'igv' && _pendingIgv) {
    var igvUrl = _pendingIgv;
    _pendingIgv = null;
    loadIgvIframe(igvUrl);
  }
  if (tab === 'svpv' && _pendingSvpv) {
    document.getElementById('viewer-svpv').src = _pendingSvpv;
    _pendingSvpv = null;
  }
  if (tab === 'ucsc-short' && _pendingUcscShort) {
    document.getElementById('ucsc-link-short').href = _pendingUcscShort.url;
    document.getElementById('viewer-ucsc-short').src = _pendingUcscShort.renderUrl;
    _pendingUcscShort = null;
  }
  if (tab === 'ucsc' && _pendingUcsc) {
    document.getElementById('ucsc-link').href = _pendingUcsc.url;
    document.getElementById('viewer-ucsc').src = _pendingUcsc.renderUrl;
    _pendingUcsc = null;
  }
});

function loadIgvIframe(url) {
  var igvIframe = document.getElementById('viewer-igv');
  var hashIdx = url.indexOf('#');
  var base = hashIdx >= 0 ? url.substring(0, hashIdx) : url;
  var hash = hashIdx >= 0 ? url.substring(hashIdx) : '';
  igvIframe.src = base + '?_t=' + Date.now() + hash;
}

function loadSample(pdfUrl, htmlUrl, rowId, ucscUrl, ucscRenderUrl) {
  var pdfIframe = document.getElementById('viewer-pdf');
  pdfIframe.src = '';
  clearTimeout(_pdfTimeout);
  _pdfTimeout = setTimeout(function() { pdfIframe.src = pdfUrl; }, 50);

  var activeTab = _activeTabs['viewer-short'];
  var igvUrl = htmlUrl + '#row=' + rowId;
  if (activeTab === 'igv') {
    loadIgvIframe(igvUrl);
    _pendingIgv = null;
  } else {
    _pendingIgv = igvUrl;
  }
  if (activeTab === 'ucsc-short') {
    document.getElementById('ucsc-link-short').href = ucscUrl;
    document.getElementById('viewer-ucsc-short').src = ucscRenderUrl;
    _pendingUcscShort = null;
  } else {
    _pendingUcscShort = { url: ucscUrl, renderUrl: ucscRenderUrl };
  }

  switchTab(document.getElementById('viewer-short'), activeTab);
}

function loadStrucSample(pdfUrl, samplotUrl, svpvUrl, ucscUrl, ucscRenderUrl) {
  var strucPdfIframe = document.getElementById('viewer-struc-pdf');
  strucPdfIframe.src = '';
  clearTimeout(_strucPdfTimeout);
  _strucPdfTimeout = setTimeout(function() { strucPdfIframe.src = pdfUrl; }, 50);

  document.getElementById('viewer-samplot').src = samplotUrl;

  var svpvIframe = document.getElementById('viewer-svpv');
  svpvIframe.src = '';
  var activeTab = _activeTabs['viewer-struc'];
  if (activeTab === 'svpv') {
    svpvIframe.src = svpvUrl;
    _pendingSvpv = null;
  } else {
    _pendingSvpv = svpvUrl;
  }

  if (activeTab === 'ucsc') {
    document.getElementById('ucsc-link').href = ucscUrl;
    document.getElementById('viewer-ucsc').src = ucscRenderUrl;
    _pendingUcsc = null;
  } else {
    _pendingUcsc = { url: ucscUrl, renderUrl: ucscRenderUrl };
  }

  switchTab(document.getElementById('viewer-struc'), activeTab);
}

</script>